---
title: "vgSalesAnalyzer"
output: html_document
date: "2025-05-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown



Import and Load Dataset

```{r}
VideoGames <- read.csv("C:/Users/alenm/OneDrive/Documents/LIS4370/vgsales.csv")

##link for dataset can be found using this link:
#https://www.kaggle.com/datasets/anandshaw2001/video-game-sales

```

Inspect and Clean Data

```{r}
str(VideoGames)
summary(VideoGames)
head(VideoGames)
tail(VideoGames)
anyNA(VideoGames)


#Data is not needed to be cleaned. No missing values found in dataset. 

```


##Function: "sales.over.time"

#Purpose:
#Aggregates video game sales by year for a selected region ("Global", "NA", "EU", "JP", or "Other").

#Output:Printed dataframe of yearly sales with a line plot demonstrating trends over time. 
```{r}

#Example Input

sales.over.time(VideoGames, "JP")

```




##Function: "top.selling.games"

#Purpose:
#Sorts and returns the top n best-selling video games in a given region.

#Output: Table of top games including name, platform, year, genre, publisher, and sales.
```{r}

#Example Input

top.selling.games(VideoGames, n = 5, region = "EU")

```


##Function: "as.videogame.object"

#Purpose:
#To convert an existing one-row data frame into an S4 object of class

#Output: Constructs a formal S4 object of class "VideoGame", with slots for name, platform, and sales.
```{r}

#Example Input

game1 <- videogame(VideoGames[1, ])
class(game1)


print(game1)

```




##Function: "build.videogame.class"

#Purpose:
#To manually create a new VideoGame S4 object by providing the individual slot values directly — name, platform, and sales.

#Output: Creates a new S4 object of class "VideoGame" using the provided values for the game's name, platform, and global sales.
```{r}

#Example Input


# Create an object
duck_hunt <- new("VideoGame", name = "Duck Hunt", platform = "NES", sales = 28.31)


getPlatform(duck_hunt)

```



##How to install vg-sales-analyzer?

#Install devtools
```{r}
install.packages("devtools")
```

#Install vg-sales-analyzer from Github
```{r}
devtools::install_github("AlenjaksAbraham/vgSalesAnalyzer")
```

#Load Package
```{r}
library(vgSalesAnalyzer)
```




